\documentclass[10pt,letterpaper,unboxed,cm]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{enumerate, comment}
\usepackage{adjustbox}

\newcommand{\st}{~\mid~}
\newcommand{\ind}{$~~~~~$}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm,algorithmicx}
\usepackage{amsmath,amssymb}


\begin{document}


\hfill{CSE 20 Summer 2021}

\hfill{Homework 2}

\hfill{Due date: Sunday, August 15, 2021 at 11:59pm}

\begin{center}
\begin{minipage}[t]{6in}
\rule{\linewidth}{2pt}

{\sc Topics} Quantifiers, Proofs and Sets
\newline

{\sc Reading} 
\begin{itemize}
\item
Sections 1.4, 1.5, 1.7, 1.8, 2.1, 2.2
\end{itemize}

{\sc Key Concepts} Predicates, domain of discourse/universe, universal quantifier, existential quantifier, negated quantifiers, nested quantifiers, Proof strategies, (counter)example, contrapositive proof, proof by contradiction, sets, subset, empty set union, intersection.
\newline

\rule{\linewidth}{2pt}
\end{minipage} \hfill

\end{center}



\textbf{In this class, unless the instructions explicitly say otherwise, you are required to justify all your answers.}

 

\begin{enumerate}
 
    
\item ({\bf 20 points})
For each statement, translate it to the form:
$$\forall x~(\underline{~~~~~~~~}~)$$
or
$$\exists x~(\underline{~~~~~~~~}~)$$

using the predicates given and state the domain. (note, you are expected to write your answer without a $\neg$ before the quantifier.)
\begin{quote}
For example: ``All dinosaurs are extinct"
\begin{itemize}
\item
$E(x)$ is ``$x$ is extinct"
\end{itemize}
Then my answer would be:
$$\forall x (E(x))$$ with the domain defined to be the set of all dinosaurs.
\end{quote}
    
\begin{enumerate}
\item
Every real number is positive or negative or zero.

\begin{itemize}
\item
$P(x)$ is ``$x$ is positive"
\item
$N(x)$ is ``$x$ is negative"
\item
$Z(x)$ is ``$x$ is zero"
\end{itemize}
\item
There are no irrational numbers that are integers
\begin{itemize}
\item
$I(x)$ is ``$x$ is an integer."
\end{itemize}
\item
It is not the case that all cats are friendly.
\begin{itemize}
\item
$F(x)$ is ``$x$ is friendly."
\end{itemize}
\item
The number 4,552,003 is not equal to the square of any integer.
\begin{itemize}
\item
$A(x)$ is ``$x^2=4,552,003$."
\end{itemize}
\item
The number 1 is a factor of any integer.
\begin{itemize}
\item
$O(x)$ is ``1 is a factor of $x$."
\end{itemize}
\item
I have a cup of coffee every morning.
\begin{itemize}
\item
$C(x)$ is ``I drink coffee on morning $x$."
\end{itemize}
\item
There is a real number between 2 and 3 that is the square root of 8.
\begin{itemize}
\item
$E(x)$ is ``$x^2=8$."
\end{itemize}
\item
The square of any rational number is rational.
\begin{itemize}
\item
$Q(x)$ is ``$x$ is rational."
\end{itemize}
\item
$-1$ is not the square of any real number.
\begin{itemize}
\item
$S(x)$ is ``$x^2=-1$."
\end{itemize}
\item
Not all rational numbers are integers.
\begin{itemize}
\item
$I(x)$ is ``$x$ is an integer."
\end{itemize}
\end{enumerate}    
    
    
 \item({\bf 16 points})
For each quantified statement and each domain, determine if it is true or false. If it is true then just say true. If it is false, then prove that it is false.

\begin{enumerate}
\item
$\forall x\exists y (x>y)$
\begin{enumerate}
\item
Domain: $\mathbb{Z}$ (the set of all integers.)
\item
Domain: $\mathbb{Z}^+$ (the set of all positive integers.)
\item
Domain: $\mathbb{Z}^-$ (the set of all negative integers.)
\item
Domain: $\mathbb{Z}^*$ (the set of all non-zero integers.)
\end{enumerate}
\item
$\forall x\forall y \exists z((x<y)\to (x<z<y))$
\begin{enumerate}
\item
Domain: $\mathbb{Z}$ (the set of all integers.)
\item
Domain: $\mathbb{Q}$ (the set of all rational numbers.)
\item
Domain: $\mathbb{R}$ (the set of all real numbers.)
\item
Domain: $\mathbb{R}^*$ (the set of all non-zero real numbers.)
\end{enumerate}
\item
$\forall x\exists y (x/y=1)$
\begin{enumerate}
\item
Domain: $\mathbb{Z^*}$ (the set of all non-zero integers.)
\item
Domain: $\mathbb{Q^*}$ (the set of all non-zero rational numbers.)
\item
Domain: $\mathbb{R}^*$ (the set of all non-zero real numbers.)
\item
Domain: $\mathbb{R}-\mathbb{Q}$ (the set of all irrational numbers.)
\end{enumerate}
\item
$\forall x\exists y (x=y^2)$
\begin{enumerate}
\item
Domain: $\mathbb{Z^+}$ (the set of all positive integers.)
\item
Domain: $\mathbb{R}-\mathbb{Q}$ (the set of all irrational numbers.)
\item
Domain: $\mathbb{R}$ (the set of all real numbers.)
\item
Domain: $\mathbb{R}^+$ (the set of all positive real numbers.)
\end{enumerate}
\end{enumerate}

\item {\bf (20 points)}
Prove the following statements using any proof strategy.
\begin{enumerate}
\item
For all integers $a,b,c$, if $a|b$ and $a|c$ then $a|(b+c)$.
\item
For all integers $a,b,c$, if $a+b$ is even and $b+c$ is even then $a+c$ is even.
\item
For all integers $n$, $n^3$ is a multiple of 9 OR $n^3+1$ is a multiple of 9 or $n^3-1$ is a multiple of 9.\\
(\emph{Hint: partition the set of all integers into {\bf Case 1:} the set of all integers of the form $3k$ for some integer $k$, {\bf Case 2:} the set of all integers of the form $3k+1$ for some integer $k$ and {\bf Case 3:} the set of all integers of the form $3k-1$ for some integer $k$.})
\item
For all positive real numbers $a$ and $b$, $\sqrt{a+b}\neq \sqrt{a} + \sqrt{b}$.

\end{enumerate}
\item {\bf (20 points)}
For each of the following statements, determine if it is true or false. If it is true, then provide a proof. If it is false then disprove it.
\begin{enumerate}
\item
For all sets $A,B$, $A\cap B\subseteq A\cup B$.
\item
For all sets $A,B$, if $A\cap B=\emptyset$ then $A\times B=\emptyset$.
\item
For all sets $A,B,C$, if $A\subseteq B$ then $A\cap B\subseteq B\cap C$
\item
For sets $A\subseteq \mathbb{R}$ and $B\subseteq \mathbb{R}$. If $A$ is closed under addition and $B$ is closed under addition then $A\cap B$ is closed under addition.
\end{enumerate}
\item {\bf (20 points)}
For each pair of sets, determine if they are {\bf disjoint, equal, proper subset} or {\bf none of the above.}
\begin{enumerate}
\item
\begin{itemize}
\item
$A=\{x\in\mathbb{Z}~|~x^2- x\geq 0\}$
\item
$B=\{x\in\mathbb{Z}~|~x-1\geq 0\}$
\end{itemize}
\item
\begin{itemize}
\item
$A=\{x\in\mathbb{Z}~|~x^2\in \mathbb{Z}\}$
\item
$B=\mathbb{Z}^{\geq 0}$
\end{itemize}
\item
\begin{itemize}
\item
$A=\{(x,y)\in\mathbb{Z}\times\mathbb{Z}~|~\text{$xy$ is odd}\}$
\item
$B=\{(x,y)\in\mathbb{Z}\times\mathbb{Z}~|~\text{$x$ is odd and $y$ is odd}\}$
\end{itemize}
\item
\begin{itemize}
\item
$A=\mathbb{R}\times\mathbb{Q}$
\item
$B=\mathbb{Q}\times\mathbb{R}$
\end{itemize}
\item
\begin{itemize}
\item
$A=\mathcal{P}(\emptyset)$
\item
$B=\{\emptyset\}$
\end{itemize}
\end{enumerate}

\end{enumerate}

\end{document}
